---
title: "Live Session Assignment 11"
author: "Jesse Chen"
date: "November 19, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fpp)
data("hsales")
```

## Question 1

a)	Plot the time series. Can you identify seasonal fluctuations and/or a trend? 


```{r cars, echo=FALSE}
plot(hsales)
```

As you can see there appears to be both a seasonal trend as well as smaller fluctuations within in the plot 

## Question 2

b)	Use a classical decomposition to calculate the trend-cycle and seasonal indices. 

```{r decompose, echo=FALSE}
fitd <- decompose(hsales)
plot(fitd)
```

## Question 3

c)	Do the results support the graphical interpretation from part (a)? 

# Answer 
Yes it does.

## Question 4

d)	Compute and plot the seasonally adjusted data. 

```{r seasadj, echo=FALSE}
fit <- stl(hsales, s.window=5)
plot(fit)
```

## Question 5

e)	Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier? 

```{r outlier, echo=FALSE}
hsales2<-ts(c(hsales[1:54],hsales[55]+200,hsales[56:275], start=c(1973,1),frequency=12))
plot(hsales2)

```

The spike mostly shows up in the remainder chart. 

## Question 6 

f)	Does it make any difference if the outlier is near the end rather than in the middle of the time series? 

No, it will only move where the spike shows up. 

## Question 7

g)	Use STL to decompose the series. 


hsales2std <- stl(hsales2, s.window = 5)
